---
title: "ISSPR"
author: "Mara Doering"
date: "2024-02-06"
output: github_document
---

```{r}
output_form <- 'svg'
knitr::opts_chunk$set(dev = output_form) # set output device to svg or pdf
```

## The Data

In this chunk we'll load the data.
```{r}
load("ISSPR_final_cleaned_data_new.rda")
str(ISSPR_data_without_overlap_metrics)
# check completeness of sessions
table(ISSPR_data_without_overlap_metrics$subj_id.x, ISSPR_data_without_overlap_metrics$session_nr)
```

Here we load the data from Experiment 1-3
```{r}
#load("~/Masterarbeit/ISSPR R Studio/ISSP_cleaned_data (1).rda")
#View(issp)

# Richard:
# To make sure that I and other people can run this script, it is important to only use file paths that are synced via Git.
# In other words, you should put this file in the project directory, so that it can be pushed to Github.
# Of course, the file 'ISSP_cleaned_data.rda' is huge (~1.4 GB), because it contains all the raw samples, and it should not be on Github.
# That's why I made a file that contains only the data.table 'issp' (since that's what you're using anyway), that we load here:
load("ISSP_data.rda")
```


Here we will load the needed libraries
```{r,message=FALSE}
library(data.table)
library(ggplot2)
library(ez)
library(assertthat)
library(psych)
library(resample)
library(mlr)
library(gsignal)
library(plyr)
library(dplyr)
library(boot)
library(ggpubr)
library(ggiraph)
library(viridisLite)
library(viridis)
library(lme4)
library(lmerTest)
library(robust)
library(fit.models)
library(pracma)
library(mgcv)
library(robustbase)
library(quickpsy)
library(scales)
library (tidyr)
library(gridExtra)
```

Some important basics before running main parts
```{r}
# first we need this: http://stackoverflow.com/questions/10738729/r-strsplit-with-multiple-unordered-split-arguments
strsplits <- function(x, splits, ...)
{
  for (split in splits)
  {
    x <- unlist(strsplit(x, split, ...))
  }
  return(x[!x == ""]) # Remove empty values (it actually returns nonempty values - dose not remove anything)
}

bin_to_numeric <- function(input, splits_used = c("\\(", "\\)", "\\[", "\\]", ",") ) {
  # this function converts output from the cut_number/cut_width - function to numeric values
  return(mean(as.numeric(strsplits(x = as.character(input), splits = splits_used))))
}

ocimTheme <- function(base_size=15, base_family="Helvetica") {
  theme_classic(base_size=base_size, base_family=base_family) %+replace%
    theme(
      # size of text
      axis.text = element_text(size = 0.9*base_size),
      legend.text = element_text(size = 0.9*base_size),
      # remove grid horizontal and vertical lines
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.background  = element_blank(),
      # panel boxes
      panel.border = element_blank(),
      axis.line = element_line(colour = "grey20"),
      # facet strips
      strip.text = element_text(size = base_size, face = "bold"),
      strip.background = element_rect(fill="transparent", colour = "transparent"),
      strip.placement = "outside",
      # legend
      legend.background = element_rect(fill="transparent", colour=NA),
      legend.key = element_rect(fill="transparent", colour=NA)
    )
}


scr.ppd <- 20.5652

experiment_colorscale <- c('#1b9e77','#d95f02','#7570b3')
```
Preparing data file
```{r}
setDT(ISSPR_data_without_overlap_metrics)
ISSPR_data_without_overlap_metrics <- ISSPR_data_without_overlap_metrics[!is.na(resp)]
issp[ , stim_dur_ms_f := ordered(stim_dur_ms)]
table(issp$stim_dur_ms, issp$stim_dur_ms_f)
issp[ , experiment_f := factor(experiment)]
```

Stimulus Duration changes to numeric
```{r}
ISSPR_data_without_overlap_metrics[ , stim_dur_ms := round(stim_dur, 2)]
ISSPR_data_without_overlap_metrics[ , stim_dur_ms_f := ordered(stim_dur_ms)]
table(ISSPR_data_without_overlap_metrics$stim_dur_ms, ISSPR_data_without_overlap_metrics$stim_dur_ms_f)
```

Here we start with the common_subj_id for Experiment 2 und Reply Experiment
```{r}
#### RICHARDs COMMENTS
# Richard: Have a look at the subject codes in the replay experiment:
table(ISSPR_data_without_overlap_metrics$subj_id.x, useNA = "ifany")
# ... so this is why indexing like this would not work (it's actually "P2")
table(ISSPR_data_without_overlap_metrics$subj_id.x=="2", useNA = "ifany")
# Fixing the naming conventions should fix the common_subj_id.
# Remember to check whether the naming worked by doing:
#table(ISSPR_data_without_overlap_metrics$subj_id.x,
       #ISSPR_data_without_overlap_metrics$common_subj_id,
       #useNA = "ifany")
#### END

###Mara COMMENTS
# I change it here and with ur last code (checking); it looks good (I guess)
###END

#first we will have the three P. which were tested for Experiment 1 and 2; Replay
issp[experiment==2 & subj_id=="10", common_subj_id := "01"]
issp[experiment==1 & subj_id=="20", common_subj_id := "01"]
ISSPR_data_without_overlap_metrics[subj_id.x=="P2", common_subj_id := "01"]

issp[experiment==2 & subj_id=="20", common_subj_id := "2"]
issp[experiment==1 & subj_id=="19", common_subj_id := "2"]
ISSPR_data_without_overlap_metrics[subj_id.x=="P3", common_subj_id := "2"]

issp[experiment==2 & subj_id=="15", common_subj_id := "3"]
issp[experiment==1 & subj_id=="23", common_subj_id := "3"]
ISSPR_data_without_overlap_metrics[subj_id.x=="P7", common_subj_id := "3"]

# here we create only for P. which were included for Experiment 2 and Replay
issp[experiment==2 & subj_id=="03", common_subj_id := "4"]
ISSPR_data_without_overlap_metrics[subj_id.x=="P5", common_subj_id := "4"]

issp[experiment==2 & subj_id=="01", common_subj_id := "5"]
ISSPR_data_without_overlap_metrics[subj_id.x=="P1", common_subj_id := "5"]

issp[experiment==2 & subj_id=="11", common_subj_id := "6"]
ISSPR_data_without_overlap_metrics[subj_id.x=="P4", common_subj_id := "6"]

issp[experiment==2 & subj_id=="12", common_subj_id := "7"]
ISSPR_data_without_overlap_metrics[subj_id.x=="P9", common_subj_id := "7"]

issp[experiment==2 & subj_id=="16", common_subj_id := "8"]
ISSPR_data_without_overlap_metrics[subj_id.x=="20", common_subj_id := "8"]

issp[experiment==2 & subj_id=="14", common_subj_id := "9"]
ISSPR_data_without_overlap_metrics[subj_id.x=="08", common_subj_id := "9"]


# check saccade experiments
table(issp$experiment, issp$common_subj_id)
# check replay experiment
table(ISSPR_data_without_overlap_metrics$experiment, ISSPR_data_without_overlap_metrics$common_subj_id)
```

Here we create one plot for Exp. 1&2 and color condition (Example)
```{r}
figure2_xlim_issp12 <- c(-50, 25)

issp12_color_correct <- issp[experiment<3,# & sac_dur_prob>=0.4 & sac_dur_prob<=0.6,
                             .(correct = mean(correct),
                               sac_display_off_latency = mean(sac_display_off_latency)),
                             by = .(experiment_f, subj_id, color_yes_f, stim_dur_ms, stim_dur_ms_f)]
issp12_color_correct[ , gm_correct := mean(correct), by = .(experiment_f)]
issp12_color_correct[ , correct.w := correct - mean(correct) + gm_correct, by = .(experiment_f, subj_id)]
issp12_color_correct_agg <- issp12_color_correct[ ,
                                                  .(correct = mean(correct.w),
                                                    correct_se = sd(correct.w) / sqrt(length(correct.w)),
                                                    sac_display_off_latency = mean(sac_display_off_latency),
                                                    sac_display_off_latency_sd = sd(sac_display_off_latency) / sqrt(length(sac_display_off_latency)) ),
                                                  by = .(experiment_f, color_yes_f, stim_dur_ms, stim_dur_ms_f)]
# plot the time course for the different scenes
p_issp12_color <- ggplot(data = issp12_color_correct_agg,
                         aes(x = sac_display_off_latency, y = correct, color = color_yes_f,
                             shape = experiment_f,
                             group = paste(experiment_f, color_yes_f))) +
  geom_vline(xintercept = 0, linetype = "dotted", alpha = 0.7) +
  geom_hline(yintercept = 0.5, linetype = "dotted", alpha = 0.7) +
  geom_errorbar(aes(ymax = correct + correct_se, ymin = correct - correct_se),
                width = 0, size = 1, alpha = 0.5) +
  geom_errorbarh(aes(xmax = sac_display_off_latency + sac_display_off_latency_sd,
                     xmin = sac_display_off_latency - sac_display_off_latency_sd),
                 height = 0, size = 1, alpha = 0.5) +
  geom_line(size = 1.5, alpha = 0.8) +
  geom_point(size = 2.5) +
  theme_classic(base_size = 12.5) + ocimTheme() +
  coord_cartesian(ylim = c(0.45, 1)) +
  scale_color_viridis_d(option = "cividis", end = 0.4, direction = -1, guide = guide_legend(reverse = TRUE)) +
  scale_shape_manual(values = c(15, 17)) +
  scale_y_continuous(expand = c(0,0)) +
  scale_x_continuous(breaks = c(-40, -30, -20, -10, 0, 10), limits = figure2_xlim_issp12) +
  labs(x = "Display offset re saccade offset [ms]", y = "Proportion scene correctly matched",
       color = "Image type", fill = "Image type", shape = "Experiment")
p_issp12_color

```

Here we start with the Prop. Correct for ISSP 1&2; by common_subj_id
```{r}
issp12_prop_correct <- issp[experiment<3,
                             .(correct = mean(correct),
                               sac_display_off_latency = mean(sac_display_off_latency)),
                             by = .(experiment_f, subj_id, common_subj_id, color_yes_f, stim_dur_ms, stim_dur_ms_f)]
issp12_prop_correct[ , gm_correct := mean(correct), by = .(experiment_f)]
issp12_prop_correct[ , correct.w := correct - mean(correct) + gm_correct, by = .(experiment_f, common_subj_id)]
issp12_prop_correct <- issp12_prop_correct[color_yes_f=="grayscale"]
issp12_prop_correct[ , sac_suppression_f:= factor("unfiltered")]
issp12_prop_correct[ , fixreplay:= ("Saccade (Exp. 1&2)")]
# if you check this, you find that all other subjects are also still included as NA:
table(issp12_prop_correct$common_subj_id, issp12_prop_correct$experiment_f, useNA="ifany")
issp12_prop_correct[is.na(common_subj_id), common_subj_id := "all others"]

# in this variable we code whether participants have a common_subj_id or not
issp12_prop_correct[common_subj_id == "all others", common_subj_id_exists := "unmatched"]
issp12_prop_correct[common_subj_id != "all others", common_subj_id_exists := "matched"]

# this has to be a population aggregate. Including common_subj_id aggregates for each subject (which is already aggregated)
issp12_prop_correct_agg <- issp12_prop_correct[ ,
                                                  .(correct = mean(correct.w),
                                                    correct_se = sd(correct.w) / sqrt(length(correct.w)),
                                                    sac_display_off_latency = mean(sac_display_off_latency),
                                                    sac_display_off_latency_sd = sd(sac_display_off_latency) / sqrt(length(sac_display_off_latency)) ),
                                                  by = .(common_subj_id_exists,
                                                         experiment_f, color_yes_f, stim_dur_ms, stim_dur_ms_f,
                                                         fixreplay, sac_suppression_f)]
```

Here we create the Plot for Prop. Correct; ISSP 1&2 and Common_subj_id

Richard: Note the command to determine figure width and height in markdown.
```{r, fig.width=15, fig.height=7}
# this is for individual subjects, only those that have a common_subj_id (N=9):
p_issp12_prop_subj <- ggplot(data = issp12_prop_correct[common_subj_id != "all others"],
                         aes(x = sac_display_off_latency, y = correct, color = sac_suppression_f,
                             shape = fixreplay,
                             group = paste(experiment_f, color_yes_f)))+
  geom_vline(xintercept = 0, linetype = "dotted", alpha = 0.7) +
  geom_hline(yintercept = 0.5, linetype = "dotted", alpha = 0.7) +
  geom_line(size = 1.5, alpha = 0.8) +
  geom_point(size = 2.5) +
  theme_classic(base_size = 12.5) + ocimTheme() +
  coord_cartesian(ylim = c(0.45, 1)) +
  scale_color_manual(values = experiment_colorscale) +
  scale_shape_manual(values = c(15, 17)) +
  scale_y_continuous(expand = c(0,0)) +
  scale_x_continuous(breaks = c(-40, -30, -20, -10, 0, 10, 20), limits = figure2_xlim_issp12) +
  labs(x = "Display offset re saccade offset [ms]", y = "Proportion scene correctly matched",
       color = "Simulated suppression", fill = "Simulated suppression", shape = "Task") +
  facet_wrap(~common_subj_id)
p_issp12_prop_subj
```

This plot contains the population aggregate for participants that are matched across experiments
(common_subj_ids 1..9) and those that are not (encoded in the variable common_subj_id_exists)
``` {r}
p_issp12_prop <- ggplot(data = issp12_prop_correct_agg,
                         aes(x = sac_display_off_latency, y = correct, color = sac_suppression_f,
                             shape = fixreplay,
                             group = paste(experiment_f, color_yes_f)))+
  geom_vline(xintercept = 0, linetype = "dotted", alpha = 0.7) +
  geom_hline(yintercept = 0.5, linetype = "dotted", alpha = 0.7) +
  geom_errorbar(aes(ymax = correct + correct_se, ymin = correct - correct_se),
                width = 0, size = 1, alpha = 0.5) +
  geom_errorbarh(aes(xmax = sac_display_off_latency + sac_display_off_latency_sd,
                     xmin = sac_display_off_latency - sac_display_off_latency_sd),
                 height = 0, size = 1, alpha = 0.5) +
  geom_line(size = 1.5, alpha = 0.8) +
  geom_point(size = 2.5) +
  theme_classic(base_size = 12.5) + ocimTheme() +
  coord_cartesian(ylim = c(0.45, 1)) +
  scale_color_manual(values = experiment_colorscale) +
  scale_shape_manual(values = c(15, 17)) +
  scale_y_continuous(expand = c(0,0)) +
  scale_x_continuous(breaks = c(-40, -30, -20, -10, 0, 10, 20), limits = figure2_xlim_issp12) +
  labs(x = "Display offset re saccade offset [ms]", y = "Proportion scene correctly matched",
       color = "Simulated suppression", fill = "Simulated suppression", shape = "Task") +
  facet_wrap(~common_subj_id_exists)
p_issp12_prop
```

Here we start making a plot that does the same for the Replay Experiment (for unfiltered vs suppression)
```{r}
# RICHARD: added subj_id.x here
ISSPR_prop_correct <- ISSPR_data_without_overlap_metrics[experiment==4,
                             .(correct = mean(correct),
                               replay_sac_display_off_latency = mean(replay_sac_display_off_latency)),
                             by = .(experiment, common_subj_id, subj_id.x, sac_suppression_f,
                                    stim_dur_ms, stim_dur_ms_f)]

ISSPR_prop_correct[ , gm_correct := mean(correct), by = .(experiment)]
ISSPR_prop_correct[ , correct.w := correct - mean(correct) + gm_correct, by = .(experiment, common_subj_id)]
str(ISSPR_prop_correct$sac_suppression_f) # Richard: Why do you do this below? You already have the correct factor
#ISSPR_prop_correct[ , sac_suppression_f:= factor ("filtered")]
# if you want to re-level, you can do this:
levels(ISSPR_prop_correct$sac_suppression_f) <- c("unfiltered", "filtered")
ISSPR_prop_correct[, fixreplay:= ("Replay (Exp. 4)")]


# if you check this, you find that all other subjects are also still included as NA:
table(ISSPR_prop_correct$common_subj_id, ISSPR_prop_correct$experiment, useNA="ifany")
ISSPR_prop_correct[is.na(common_subj_id), common_subj_id := "all others"]
table(ISSPR_data_without_overlap_metrics$common_subj_id, useNA = "ifany")

# in this variable we code whether participants have a common_subj_id or not
ISSPR_prop_correct[common_subj_id == "all others", common_subj_id_exists_replay := "unmatched"]
ISSPR_prop_correct[common_subj_id != "all others", common_subj_id_exists_replay := "matched"]
table(ISSPR_prop_correct$common_subj_id, ISSPR_prop_correct$common_subj_id_exists_replay, useNA = "ifany")

# Replay: population-level aggregate
ISSPR_prop_correct_agg <- ISSPR_prop_correct[ ,
                                                  .(correct = mean(correct.w),
                                                    correct_se = sd(correct.w) / sqrt(length(correct.w)),
                                                    replay_sac_display_off_latency = mean(replay_sac_display_off_latency),
                                                    replay_sac_display_off_latency_sd = sd(replay_sac_display_off_latency) /
                                                      sqrt(length(replay_sac_display_off_latency)) ),
                                                  by = .(common_subj_id_exists_replay, experiment,
                                                         stim_dur_ms, stim_dur_ms_f, fixreplay,
                                                         sac_suppression_f)]
ISSPR_prop_correct_agg
```

Here we create the Plot for Prop. Correct; ISSP Replay and common_subj_id

Mara Comment: Here is the same problem; the legend changed when Iam using (scale_color_manual(values = experiment_colorscale)), what is the mistake here?

Richard Response: Not sure what you mean. You did not use the command above but a different one (commented below), so I would not be surprised to see the color code change... it should be fixed now.

```{r, fig.width=15, fig.height=7}
ISSPR_prop_subj <- ggplot(data = ISSPR_prop_correct[common_subj_id != "all others"],
                         aes(x = replay_sac_display_off_latency, y = correct, color = sac_suppression_f,
                             shape = fixreplay,
                             group = paste(experiment, sac_suppression_f)))+
  geom_vline(xintercept = 0, linetype = "dotted", alpha = 0.7) +
  geom_hline(yintercept = 0.5, linetype = "dotted", alpha = 0.7) +
  geom_line(size = 1.5, alpha = 0.8) +
  geom_point(size = 2.5) +
  theme_classic(base_size = 12.5) + ocimTheme() +
  coord_cartesian(ylim = c(0.45, 1)) +
  #scale_color_viridis_d(option = "cividis", end = 0.4, direction = -1, guide = guide_legend(reverse = TRUE)) +
  scale_color_manual(values = experiment_colorscale) + 
  scale_shape_manual(values = c(15, 17)) +
  scale_y_continuous(expand = c(0,0)) +
  scale_x_continuous(breaks = c(-40, -30, -20, -10, 0, 10, 20), limits = figure2_xlim_issp12) +
  labs(x = "Display offset re saccade offset [ms]", y = "Proportion scene correctly matched",
       color = "Simulated suppression", fill = "Simulated suppression", shape = "Task") +
  facet_wrap(~common_subj_id)

ISSPR_prop_subj
```


Here, this plot contains the population aggregate for participants for Replay Condition
```{r, fig.width=15, fig.height=7}
ISSPR_prop <- ggplot(data = ISSPR_prop_correct_agg,
                         aes(x = replay_sac_display_off_latency, y = correct, color = sac_suppression_f,
                             shape = fixreplay,
                             group = paste(experiment, sac_suppression_f)))+
  geom_vline(xintercept = 0, linetype = "dotted", alpha = 0.7) +
  geom_hline(yintercept = 0.5, linetype = "dotted", alpha = 0.7) +
  geom_errorbar(aes(ymax = correct + correct_se, ymin = correct - correct_se),
                width = 0, size = 1, alpha = 0.5) +
  geom_errorbarh(aes(xmax = replay_sac_display_off_latency + replay_sac_display_off_latency_sd,
                     xmin = replay_sac_display_off_latency - replay_sac_display_off_latency_sd),
                 height = 0, size = 1, alpha = 0.5) +
  geom_line(size = 1.5, alpha = 0.8) +
  geom_point(size = 2.5) +
  theme_classic(base_size = 12.5) + ocimTheme() +
  coord_cartesian(ylim = c(0.45, 1)) +
  scale_color_manual(values = experiment_colorscale, guide = guide_legend(reverse = TRUE)) +
  scale_shape_manual(values = c(15, 17)) +
  scale_y_continuous(expand = c(0,0)) +
  scale_x_continuous(breaks = c(-40, -30, -20, -10, 0, 10, 20), limits = figure2_xlim_issp12) +
  labs(x = "Display offset re saccade offset [ms]", y = "Proportion scene correctly matched",
       color = "Simulated suppression", fill = "Simulated suppression", shape = "Task") +
  facet_wrap(~common_subj_id_exists_replay)

ISSPR_prop
```

Here we combine saccade and replay condition in one Plot for N=9
```{r, fig.width=15, fig.height=7}
ggplot()+
  geom_point(data=ISSPR_prop_correct[common_subj_id != "all others"],
             aes(x = replay_sac_display_off_latency, y = correct, color = sac_suppression_f,
                 shape = fixreplay,
                 group = paste(experiment, sac_suppression_f)))+
  geom_vline(xintercept = 0, linetype = "dotted", alpha = 0.7) +
  geom_hline(yintercept = 0.5, linetype = "dotted", alpha = 0.7) +
  geom_line(data=ISSPR_prop_correct[common_subj_id != "all others"],
             aes(x = replay_sac_display_off_latency, y = correct, color = sac_suppression_f,
                 linetype = fixreplay,
                 group = paste(experiment, sac_suppression_f)),
            size = 1.5, alpha = 0.8) +
  labs(x = "Display offset re saccade offset [ms]", y = "Proportion scene correctly matched",
       color = "Simulated suppression", fill = "Simulated suppression", shape = "Task") +
  geom_point(data= issp12_prop_correct[common_subj_id != "all others"],
             aes(x = sac_display_off_latency, y = correct, color = sac_suppression_f,
                 shape = fixreplay,
                 group = paste(experiment_f, color_yes_f)))+
  geom_vline(xintercept = 0, linetype = "dotted", alpha = 0.7) +
  geom_hline(yintercept = 0.5, linetype = "dotted", alpha = 0.7) +
  geom_line(data= issp12_prop_correct[common_subj_id != "all others"],
             aes(x = sac_display_off_latency, y = correct, color = sac_suppression_f,
                 linetype = fixreplay,
                 group = paste(experiment_f, color_yes_f)),
            size = 1.5, alpha = 0.8) +
  theme_classic(base_size = 12.5) + ocimTheme() +
  coord_cartesian(ylim = c(0.45, 1)) +
  scale_color_manual(values = experiment_colorscale, guide = guide_legend(reverse = TRUE)) +
  scale_shape_manual(values = c(15, 17)) +
  scale_y_continuous(expand = c(0,0)) +
  scale_x_continuous(breaks = c(-40, -30, -20, -10, 0, 10, 20)) +
  labs(x = "Display offset re saccade offset [ms]", y = "Proportion scene correctly matched",
       color = "Simulated suppression", fill = "Simulated suppression", shape = "Task",
       linetype = "Task") +
  facet_wrap(~common_subj_id)
```

Here I want to combine the plots of the population aggregate for participants that are matched across experiments (common_subj_ids 1-9) and those that are not
```{r, fig.width=15, fig.height=7}
issp12_prop_correct_agg[ , common_subj_id_exists_replay := common_subj_id_exists]

ggplot()+
  geom_vline(xintercept = 0, linetype = "dotted", alpha = 0.7) +
  geom_hline(yintercept = 0.5, linetype = "dotted", alpha = 0.7) +
  geom_point(data=issp12_prop_correct_agg,
             aes(x = sac_display_off_latency, y = correct, color = sac_suppression_f,
                 shape = fixreplay,
                 group = paste(experiment_f, color_yes_f)), size = 2)+
  geom_line(data=issp12_prop_correct_agg,
            aes(x = sac_display_off_latency, y = correct, color = sac_suppression_f,
                linetype = fixreplay,
                group = paste(experiment_f, color_yes_f)),
            size = 1.5, alpha = 0.8) +
  labs(x = "Display offset re saccade offset [ms]", y = "Proportion scene correctly matched",
       color = "Simulated suppression", fill = "Simulated suppression", shape = "Task") +
  geom_point(data = ISSPR_prop_correct_agg,
             aes(x = replay_sac_display_off_latency, y = correct, color = sac_suppression_f,
                 shape = fixreplay,
                 group = paste(experiment, sac_suppression_f)), size = 2) +
  geom_line(data = ISSPR_prop_correct_agg,
             aes(x = replay_sac_display_off_latency, y = correct, color = sac_suppression_f,
                 linetype = fixreplay,
                 group = paste(experiment, sac_suppression_f)),
            size = 1.5, alpha = 0.8) +
  geom_errorbar(data = ISSPR_prop_correct_agg,
                aes(x = replay_sac_display_off_latency, color = sac_suppression_f,
                    ymax = correct + correct_se, ymin = correct - correct_se),
                width = 0, size = 1, alpha = 1) +
  geom_errorbarh(data = ISSPR_prop_correct_agg,
                 aes(y = correct, color = sac_suppression_f,
                     xmax = replay_sac_display_off_latency + replay_sac_display_off_latency_sd,
                     xmin = replay_sac_display_off_latency - replay_sac_display_off_latency_sd),
                 height = 0, size = 1, alpha = 1) +
  theme_classic(base_size = 12.5) + ocimTheme() +
  coord_cartesian(ylim = c(0.45, 1)) +
  scale_color_manual(values = experiment_colorscale, guide = guide_legend(reverse = TRUE))+
  scale_shape_manual(values = c(15, 17)) +
  scale_linetype_manual(values = rev(c("dashed", "solid"))) +
  scale_y_continuous(expand = c(0,0)) +
  scale_x_continuous(breaks = c(-40, -30, -20, -10, 0, 10, 20), limits = figure2_xlim_issp12) +
  labs(x = "Display offset re saccade offset [ms]", y = "Proportion scene correctly matched",
       color = "Simulated suppression", fill = "Simulated suppression", shape = "Task",
       linetype = "Task") +
  facet_wrap(~common_subj_id_exists_replay)
```

Here we start with statistic differences between saccade/replay condition
First: within subject (VP (N=9) data from Exp 2 + Replay) for the UNFILTERED condition.
Mara Comment: Would it be better to different here excatly that is is only Saccade (Exp. 2) in the legend?

Richard Comment: Yes, saccade (Exp. 2) would certainly be more suitable. But I guess you can edit this manually later when you export the figure as svg or pdf. 
Furthermore, if you use ezPlot, then you should try to keep the style consistent to your other figures. Especially, different color schemes suggest that something else is plotted there. As you have seen below, I have tried my best to adjust the style to match the figure above, but line and point size is still not the same. Whatever you do in this chunk, please also apply to all the subsequent ezPlot commands.

Ok. I tried to add the style first to all subsequent ezPlots. With the legend and the color Iam still unsure here.

Finally, one important thing: Here you use the same color scale you use to compare original vs suppressed (or unfiltered vs filtered, you would have to decide for one way) to compare experiments! That is extremely confusing and should really be avoided. When you compare viewing conditions (saccade vs replay) you should really use a different color scale.

```{r}
# okay, below we merge the data of Experiment 2 and Replay (n=9) with unfiltered condition
table(issp$experiment, issp$common_subj_id, useNA = "ifany")
table(issp$stim_dur_ms_f, useNA = "ifany")
common_subj_id_subset_issp12 <- issp12_prop_correct[common_subj_id!="all others" & stim_dur_ms < 60 &
                                                      experiment_f == "2"]
table(common_subj_id_subset_issp12$experiment, common_subj_id_subset_issp12$common_subj_id, useNA = "ifany")
table(common_subj_id_subset_issp12$stim_dur_ms, common_subj_id_subset_issp12$common_subj_id, useNA = "ifany")

# Replay Experiment=4, common_subj_id = 1-9
table(ISSPR_prop_correct$experiment, ISSPR_prop_correct$common_subj_id,
      ISSPR_prop_correct$common_subj_id_exists_replay, useNA = "ifany")
table(ISSPR_data_without_overlap_metrics$stim_dur_ms, useNA = "ifany")
common_subj_id_subset_ISSPR <- ISSPR_prop_correct[common_subj_id!="all others" &
                                                    stim_dur_ms > 30 & stim_dur_ms < 60 &
                                                    sac_suppression_f=="unfiltered"] # choose condition here!
table(common_subj_id_subset_ISSPR$experiment, common_subj_id_subset_ISSPR$common_subj_id)
table(common_subj_id_subset_ISSPR$stim_dur_ms, common_subj_id_subset_ISSPR$common_subj_id)

# combine the two sets to perform an ANOVA
subset_ISSPexperiments <- rbindlist(list(common_subj_id_subset_issp12 , common_subj_id_subset_ISSPR),
                                    fill = TRUE)
# verify that all conditions are comparable (we need one value in each cell)
table(subset_ISSPexperiments$common_subj_id, subset_ISSPexperiments$stim_dur_ms,
      subset_ISSPexperiments$fixreplay, useNA = "ifany")

# perform ANOVA
ezANOVA(data = subset_ISSPexperiments, wid = .(common_subj_id), dv = .(correct),
        within = .(fixreplay, stim_dur_ms_f), detailed = TRUE)
ezStats(data = subset_ISSPexperiments, wid = .(common_subj_id), dv = .(correct),
        within_full = .(fixreplay, stim_dur_ms_f), within = .(fixreplay))


# plot to evaluate ANOVA results
ezPlot(data = subset_ISSPexperiments, wid = .(common_subj_id), dv = .(correct),
       within = .(fixreplay, stim_dur_ms_f),
       x = .(stim_dur_ms_f), split = .(fixreplay), 
       bar_width = 0.00001
       ) +
  labs(y = "Proportion scene correctly matched")+
  labs(x = "Display Duration [ms]",
       color = "Task",
       linetype = "Task",
       shape = "Task", 
       title = "Saccade (Exp. 2) vs Replay original"
  ) +
  geom_hline(yintercept = 0.5, linetype = "dotted") + 
  scale_linetype_manual(values = c("solid", "dashed")) + 
  scale_shape_manual(values = c(15, 17)) +
  theme_classic(base_size = 12.5) + ocimTheme() +
  coord_cartesian(ylim = c(0.45, 1)) +
  scale_color_manual(values = c(experiment_colorscale[1], experiment_colorscale[1]), 
                     guide = guide_legend(reverse = TRUE))
  
```


Second: within subject (VP (N=9) data from Exp 2 + Replay) for the FILTERED condition.
Mama Comment: Same question like above; Legend changes?
```{r}
common_subj_id_subset_ISSPR_filt <- ISSPR_prop_correct[common_subj_id!="all others" &
                                                         stim_dur_ms > 30 & stim_dur_ms < 60 &
                                                         sac_suppression_f=="filtered"] # choose condition

# okay, merge
subset_ISSPexperiments_filt <- rbindlist(list(common_subj_id_subset_issp12,
                                              common_subj_id_subset_ISSPR_filt),
                                         fill = TRUE)
# make sure we have the variable stim_dur_ms_f for ANOVA in both frames
table(subset_ISSPexperiments_filt$common_subj_id, subset_ISSPexperiments_filt$stim_dur_ms_f,
      subset_ISSPexperiments_filt$fixreplay, useNA = "ifany")

# perform ANOVA
ezANOVA(data = subset_ISSPexperiments_filt, wid = .(common_subj_id), dv = .(correct),
        within = .(fixreplay, stim_dur_ms_f), detailed = TRUE)

ezStats(data = subset_ISSPexperiments_filt, wid = .(common_subj_id), dv = .(correct),
        within_full = .(fixreplay, stim_dur_ms_f), within = .(fixreplay))

matchedsuppressed <- ezPlot(data = subset_ISSPexperiments_filt, wid = .(common_subj_id), dv = .(correct),
       within = .(fixreplay, stim_dur_ms_f),
       x = .(stim_dur_ms_f), split = .(fixreplay), 
       bar_width = 0.00001)+
  labs(y = "Proportion scene correctly matched")+
  labs(x = "Display Duration [ms]",
       color = "Task",
       linetype = "Task",
       shape = "Task", 
       title = "Saccade (Exp. 2) vs Replay suppressed"
  ) +
  geom_hline(yintercept = 0.5, linetype = "dotted") + 
  scale_linetype_manual(values = c("solid", "dashed")) + 
  scale_shape_manual(values = c(15, 17)) +
  theme_classic(base_size = 12.5) + ocimTheme() +
  coord_cartesian(ylim = c(0.45, 1)) +
  scale_color_manual(values = c(experiment_colorscale[2], experiment_colorscale[1]), 
                     guide = guide_legend(reverse = TRUE))
matchedsuppressed 



```

Second: within subject (VP (N=9) data from Exp 2 + Replay) for the UNFILTERED condition.
```{r}
common_subj_id_subset_ISSPR_filt <- ISSPR_prop_correct[common_subj_id!="all others" &
                                                         stim_dur_ms > 30 & stim_dur_ms < 60 &
                                                         sac_suppression_f=="unfiltered"] # choose condition

# okay, merge
subset_ISSPexperiments_filt <- rbindlist(list(common_subj_id_subset_issp12,
                                              common_subj_id_subset_ISSPR_filt),
                                         fill = TRUE)
# make sure we have the variable stim_dur_ms_f for ANOVA in both frames
table(subset_ISSPexperiments_filt$common_subj_id, subset_ISSPexperiments_filt$stim_dur_ms_f,
      subset_ISSPexperiments_filt$fixreplay, useNA = "ifany")

# perform ANOVA
ezANOVA(data = subset_ISSPexperiments_filt, wid = .(common_subj_id), dv = .(correct),
        within = .(fixreplay, stim_dur_ms_f), detailed = TRUE)

ezStats(data = subset_ISSPexperiments_filt, wid = .(common_subj_id), dv = .(correct),
        within_full = .(fixreplay, stim_dur_ms_f), within = .(fixreplay))

matchedoriginal <- ezPlot(data = subset_ISSPexperiments_filt, wid = .(common_subj_id), dv = .(correct),
       within = .(fixreplay, stim_dur_ms_f),
       x = .(stim_dur_ms_f), split = .(fixreplay), 
       bar_width = 0.00001)+
  labs(y = "Proportion scene correctly matched")+
  labs(x = "Display Duration [ms]",
       color = "Task",
       linetype = "Task",
       shape = "Task", 
       title = "Saccade (Exp. 2) vs Replay Original"
  ) +
  geom_hline(yintercept = 0.5, linetype = "dotted") + 
  scale_linetype_manual(values = c("solid", "dashed")) + 
  scale_shape_manual(values = c(15, 17)) +
  theme_classic(base_size = 12.5) + ocimTheme() +
  coord_cartesian(ylim = c(0.45, 1)) +
  scale_color_manual(values = c(experiment_colorscale[1], experiment_colorscale[1]), 
                     guide = guide_legend(reverse = TRUE))

matchedoriginal

```




Subj. not in both conditions; between (bw) design N=11; no-common subjects!
"Original condition"
```{r}
# not-common subjects in saccade exp
common_subj_id_subset_issp12_bw <- issp12_prop_correct[common_subj_id== "all others" &
                                                         stim_dur_ms < 60 & experiment_f == "2"]
# recode the subj_id
common_subj_id_subset_issp12_bw[ , subj_id := as.character(as.numeric(as.ordered(subj_id)))] # 1-11
table(common_subj_id_subset_issp12_bw$experiment, common_subj_id_subset_issp12_bw$subj_id,
      common_subj_id_subset_issp12_bw$common_subj_id)
table(common_subj_id_subset_issp12_bw$stim_dur_ms, common_subj_id_subset_issp12_bw$subj_id)

# not-common subjects in replay; ISSPR
ISSPR_data_without_overlap_metrics[ , subj_id := subj_id.x]
table(ISSPR_data_without_overlap_metrics$stim_dur_ms, ISSPR_data_without_overlap_metrics$subj_id)
ISSPR_allothers_correct <- ISSPR_data_without_overlap_metrics[is.na(common_subj_id) & # only those who do not have a common subj id
                                                                experiment==4 &
                                                                stim_dur_ms > 30 & stim_dur_ms < 60,
                             .(correct = mean(correct),
                               replay_sac_display_off_latency = mean(replay_sac_display_off_latency)),
                             by = .(experiment, subj_id, sac_suppression_f, stim_dur_ms, stim_dur_ms_f)]
ISSPR_allothers_correct$fixreplay <- "Replay (Exp. 4)"

# recode the subj_id
ISSPR_allothers_correct[ , subj_id := as.character(as.numeric(as.ordered(subj_id)))] # 1-11
table(ISSPR_allothers_correct$stim_dur_ms, ISSPR_allothers_correct$subj_id)

# within-subj variance here
ISSPR_allothers_correct[ , gm_correct := mean(correct), by = .(experiment)]
ISSPR_allothers_correct[ , correct.w := correct - mean(correct) + gm_correct, by = .(experiment, subj_id)]

# combine the two sets to perform an ANOVA,  Original Condition for filtered images
# DECIDE HERE WHETHER ORIGINAL OR FILTERED IMAGES SHOULD BE COMPARED WITH SACCADE CONDITION (original vs suppressed)
subset_ISSPexperiments_bw <- rbindlist(list(common_subj_id_subset_issp12_bw,
                                            ISSPR_allothers_correct[sac_suppression_f=="original"]),
                                    fill = TRUE)

# verify that all conditions are comparable and we have the same number of (independent) subjects
table(subset_ISSPexperiments_bw$subj_id, subset_ISSPexperiments_bw$stim_dur_ms,
      subset_ISSPexperiments_bw$fixreplay, useNA = "ifany")

# convert subj_id to factor
subset_ISSPexperiments_bw[ , subj_id := factor(subj_id)]
subset_ISSPexperiments_bw[ , fixreplay_f := factor(fixreplay)]
subset_ISSPexperiments_bw[ , stim_dur_ms_f := droplevels(stim_dur_ms_f)]
table(subset_ISSPexperiments_bw$subj_id, subset_ISSPexperiments_bw$stim_dur_ms_f)

# perform ANOVA
ezANOVA(data = subset_ISSPexperiments_bw, wid = .(subj_id), dv = .(correct),
        between = .(fixreplay),
        within = .(stim_dur_ms_f),
        detailed = TRUE)


#ezStats(data = subset_ISSPexperiments_bw, wid = .(subj_id), dv = .(correct),
       # between = .(fixreplay), within = .(stim_dur_ms_f))

ezStats(data = subset_ISSPexperiments_bw, wid = .(subj_id), dv = .(correct),
        within_full = .(fixreplay, stim_dur_ms_f), within = .(fixreplay))

# plot to evaluate ANOVA results
unmatchedoriginalplot <- ezPlot(data = subset_ISSPexperiments_bw, wid = .(subj_id), dv = .(correct),
       between = .(fixreplay), within = .(stim_dur_ms_f),
       x = .(stim_dur_ms_f), split = .(fixreplay), bar_width=0.00001)+scale_color_manual(values = experiment_colorscale)+
      labs(y = "Proportion scene correctly matched")+
      labs(x = "Display Duration [ms]",
              color = "Task",
       linetype = "Task",
       shape = "Task", 
       title = "Subj. not in both conditions vs. Replay original"
  ) +
  geom_hline(yintercept = 0.5, linetype = "dotted") + 
  scale_linetype_manual(values = c("solid", "dashed")) + 
  scale_shape_manual(values = c(15, 17)) +
  theme_classic(base_size = 12.5) + ocimTheme() +
  coord_cartesian(ylim = c(0.45, 1)) +
  scale_color_manual(values = c(experiment_colorscale[1], experiment_colorscale[1]), 
                     guide = guide_legend(reverse = TRUE))
           
           
unmatchedoriginalplot           
           
    

```
Subj. not in both conditions; between (bw) design N=11; no-common subjects!
"Suppressed condition"
``` {r}
# combine the two sets to perform an ANOVA,  Original Condition for filtered images
subset_ISSPexperiments_bw_sup <- rbindlist(list(common_subj_id_subset_issp12_bw,
                                            ISSPR_allothers_correct[sac_suppression_f=="suppressed"]),
                                    fill = TRUE)

# verify that all conditions are comparable and we have the same number of (independent) subjects
table(subset_ISSPexperiments_bw_sup$subj_id, subset_ISSPexperiments_bw$stim_dur_ms,
      subset_ISSPexperiments_bw_sup$fixreplay, useNA = "ifany")

# convert subj_id to factor
subset_ISSPexperiments_bw_sup[ , subj_id := factor(subj_id)]
subset_ISSPexperiments_bw_sup[ , fixreplay_f := factor(fixreplay)]
subset_ISSPexperiments_bw_sup[ , stim_dur_ms_f := droplevels(stim_dur_ms_f)]

table(subset_ISSPexperiments_bw_sup$subj_id, subset_ISSPexperiments_bw_sup$stim_dur_ms_f)

# perform ANOVA
ezANOVA(data = subset_ISSPexperiments_bw_sup, wid = .(subj_id), dv = .(correct),
        between = .(fixreplay),
        within = .(stim_dur_ms_f),
        detailed = TRUE)

#ezStats(data = subset_ISSPexperiments_bw_sup, wid = .(subj_id), dv = .(correct),
       # between = .(fixreplay), within = .(stim_dur_ms_f))

ezStats(data = subset_ISSPexperiments_bw_sup, wid = .(subj_id), dv = .(correct),
        within_full = .(fixreplay, stim_dur_ms_f), within = .(fixreplay))


# plot to evaluate ANOVA results
unmatchedsuppressedplot <- ezPlot(data = subset_ISSPexperiments_bw_sup, wid = .(subj_id), dv = .(correct),
       between = .(fixreplay), within = .(stim_dur_ms_f),
       x = .(stim_dur_ms_f), split = .(fixreplay), bar_width=0.00001)+scale_color_manual(values = experiment_colorscale)+
      labs(y = "Proportion scene correctly matched")+
       labs(x = "Display Duration [ms]",
      color = "Task",
       linetype = "Task",
       shape = "Task", 
       title = "Subj. not in both conditions vs. Replay suppressed"
  ) +
  geom_hline(yintercept = 0.5, linetype = "dotted") + 
  scale_linetype_manual(values = c("solid", "dashed")) + 
  scale_shape_manual(values = c(15, 17)) +
  theme_classic(base_size = 12.5) + ocimTheme() +
  coord_cartesian(ylim = c(0.45, 1)) +
  scale_color_manual(values = c(experiment_colorscale[2], experiment_colorscale[1]), 
                     guide = guide_legend(reverse = TRUE))

unmatchedsuppressedplot


```
Here we start "replay-ISSP 1& 2 -within": N=3 mit Faktor stim_dur_ms (8.33-58.33, 7 levels).
So who are the subjects that were tested in all three experiments? It's 1-3 by the definition at the top!
TO DO: do the above for unfiltered vs filtered conditions- change it for the two plots for the thesis!
Mara Comment: Here I have no p[GG] values; also write it in the docs document (Final_MT)

Richard: Well, yes, apparently there are too few subjects for assumption tests. You can state that no p[GG] were available and why. ORIGINAL 

```{r}
# saccade experiments
common_three_sac <- issp12_prop_correct[(common_subj_id=="01" | common_subj_id=="2" | common_subj_id=="3") &
                                          stim_dur_ms < 60]
table(common_three_sac$common_subj_id, common_three_sac$stim_dur_ms)
# as you can see now, people have 2 values at 33.33 - we can take the average here
common_three_sac <- common_three_sac[ , .(correct = mean(correct)),
                                      by = .(fixreplay, common_subj_id, stim_dur_ms, stim_dur_ms_f)]
table(common_three_sac$common_subj_id, common_three_sac$stim_dur_ms)

# replay experiments
common_three_replay <- ISSPR_prop_correct[(common_subj_id=="01" | common_subj_id=="2" | common_subj_id=="3") &
                                            stim_dur_ms < 60 &
                                            sac_suppression_f=="unfiltered"] # choose condition here!
table(common_three_replay$common_subj_id, common_three_replay$stim_dur_ms)

# combine the two sets to perform an ANOVA
common_three <- rbindlist(list(common_three_sac, common_three_replay),
                                    fill = TRUE)
table(common_three$common_subj_id, common_three$stim_dur_ms_f, common_three$fixreplay)

# here I make smth wrong like above (between design); ANOVA did not work
# RICHARD: experiment 1 has 3 common subjects, experiment 2 has 9. That's why it did not work. See fix above
## perform ANOVA
# use type 1 ANOVA, as we have too little subjects for assumption tests
# use ANOVA once for filtered and once for unfiltered condition for thesis!
ezANOVA(data = common_three, wid = .(common_subj_id), dv = .(correct),
        within = .(fixreplay, stim_dur_ms_f), detailed = TRUE, type = 1)

#also take care here, if changing the condition (filtered. vs unfiltered)
ezStats(data = common_three, wid = .(common_subj_id), dv = .(correct),
        within_full = .(fixreplay, stim_dur_ms_f), within = .(fixreplay), type = 1)

#ezStats(data = common_three, wid = .(common_subj_id), dv = .(correct),
        #within = .(fixreplay, stim_dur_ms_f), type = 1)

# plot to evaluate ANOVA results
allexporiginal <- ezPlot(data = common_three, wid = .(common_subj_id), dv = .(correct),
       within = .(fixreplay, stim_dur_ms_f),
       x = .(stim_dur_ms_f), split = .(fixreplay) , bar_width=0.00001, type = 1)+scale_color_manual(values = experiment_colorscale)+ labs(y = "Proportion scene correctly matched")+
    labs(x = "Display Duration [ms]",
      color = "Task",
       linetype = "Task",
       shape = "Task", 
       title = "All Experiments vs. Replay Original"
  ) +
  geom_hline(yintercept = 0.5, linetype = "dotted") + 
  scale_linetype_manual(values = c("solid", "dashed")) + 
  scale_shape_manual(values = c(15, 17)) +
  theme_classic(base_size = 12.5) + ocimTheme() +
  coord_cartesian(ylim = c(0.45, 1)) +
  scale_color_manual(values = c(experiment_colorscale[1], experiment_colorscale[1]), 
                     guide = guide_legend(reverse = TRUE))


allexporiginal 

```

```{r}
# saccade experiments
common_three_sac <- issp12_prop_correct[(common_subj_id=="01" | common_subj_id=="2" | common_subj_id=="3") &
                                          stim_dur_ms < 60]
table(common_three_sac$common_subj_id, common_three_sac$stim_dur_ms)
# as you can see now, people have 2 values at 33.33 - we can take the average here
common_three_sac <- common_three_sac[ , .(correct = mean(correct)),
                                      by = .(fixreplay, common_subj_id, stim_dur_ms, stim_dur_ms_f)]
table(common_three_sac$common_subj_id, common_three_sac$stim_dur_ms)

# replay experiments
common_three_replay <- ISSPR_prop_correct[(common_subj_id=="01" | common_subj_id=="2" | common_subj_id=="3") &
                                            stim_dur_ms < 60 &
                                            sac_suppression_f=="filtered"] # choose condition here!
table(common_three_replay$common_subj_id, common_three_replay$stim_dur_ms)

# combine the two sets to perform an ANOVA
common_three <- rbindlist(list(common_three_sac, common_three_replay),
                                    fill = TRUE)
table(common_three$common_subj_id, common_three$stim_dur_ms_f, common_three$fixreplay)

# here I make smth wrong like above (between design); ANOVA did not work
# RICHARD: experiment 1 has 3 common subjects, experiment 2 has 9. That's why it did not work. See fix above
## perform ANOVA
# use type 1 ANOVA, as we have too little subjects for assumption tests
# use ANOVA once for filtered and once for unfiltered condition for thesis!
ezANOVA(data = common_three, wid = .(common_subj_id), dv = .(correct),
        within = .(fixreplay, stim_dur_ms_f), detailed = TRUE, type = 1)

#also take care here, if changing the condition (filtered. vs unfiltered)
ezStats(data = common_three, wid = .(common_subj_id), dv = .(correct),
        within_full = .(fixreplay, stim_dur_ms_f), within = .(fixreplay), type = 1)

#ezStats(data = common_three, wid = .(common_subj_id), dv = .(correct),
        #within = .(fixreplay, stim_dur_ms_f), type = 1)

# plot to evaluate ANOVA results
allexsuppressed <- ezPlot(data = common_three, wid = .(common_subj_id), dv = .(correct),
       within = .(fixreplay, stim_dur_ms_f),
       x = .(stim_dur_ms_f), split = .(fixreplay) , bar_width=0.00001, type = 1)+scale_color_manual(values = experiment_colorscale)+ labs(y = "Proportion scene correctly matched")+
    labs(x = "Display Duration [ms]",
      color = "Task",
       linetype = "Task",
       shape = "Task", 
       title = "All Experiments vs. Replay Suppressed"
  ) +
  geom_hline(yintercept = 0.5, linetype = "dotted") + 
  scale_linetype_manual(values = c("solid", "dashed")) + 
  scale_shape_manual(values = c(15, 17)) +
  theme_classic(base_size = 12.5) + ocimTheme() +
  coord_cartesian(ylim = c(0.45, 1)) +
  scale_color_manual(values = c(experiment_colorscale[2], experiment_colorscale[1]), 
                     guide = guide_legend(reverse = TRUE))


allexsuppressed
```
Here I wanna grid the Plots; six total for the different conditions
```{r}
totalplot <- plot_grid(matchedoriginal, matchedsuppressed, unmatchedoriginalplot, unmatchedsuppressedplot, allexporiginal, allexsuppressed, 
                                         nrow = 3, align = "hv", axis = "tblr")
totalplot
```

``` 
Here I preparing for "proportion correct" by subject (N=20)
```{r}
ISSPR_data_without_overlap_metrics[ , .(prop_correct = mean(correct)),
  by = .(subj_id.x)]

prop_correct_subj_replay <- ISSPR_data_without_overlap_metrics[ , .(prop_correct = mean(correct)), by = .(subj_id.x, sac_suppression_f, stim_dur)][order(subj_id.x, sac_suppression_f, stim_dur)]

```

Plot for proportion correct by image condition and subject (N=20)
```{r, fig.width=15, fig.height=7}
p_prop_correct_subj_replay <- ggplot(data = prop_correct_subj_replay,
                              aes(x = stim_dur, y = prop_correct,
                                  color = sac_suppression_f, group = sac_suppression_f)) +
  geom_point() + geom_line() + geom_hline(yintercept = 0.5,linetype='dashed')+
  theme_classic() +
  labs(x = "Presentation duration [ms]", y = "Proportion scence correctly matched",
       color = "Simulated suppression") +
  facet_wrap(~subj_id.x)

p_prop_correct_subj_replay
```

Here we will run the ezANOVA 1 for proportion correct
```{r}
#important here (factors)
prop_correct_subj_replay$stim_dur <- factor(prop_correct_subj_replay$stim_dur)
prop_correct_subj_replay$subj_id.x <- factor(prop_correct_subj_replay$subj_id.x)

anov_prop_replay <- ezANOVA(data = prop_correct_subj_replay, dv =.(prop_correct), wid = .(subj_id.x),
                     within=.(sac_suppression_f,stim_dur),
                     detailed = TRUE)

ezStats(data = prop_correct_subj_replay, wid = .(subj_id.x), dv = .(prop_correct),
        within_full = .(sac_suppression_f, stim_dur), within = .(sac_suppression_f))

#ezStats(data = prop_correct_subj_replay[sac_suppression_f == "original", ],
      #  wid = .(subj_id.x), dv = .(prop_correct),
      #  within = .(stim_dur))

#ezStats(data = prop_correct_subj_replay[sac_suppression_f == "original", ],
                               #  wid = .(subj_id.x), dv = .(prop_correct),
                                 #within_full = .(stim_dur), within = .(stim_dur), type = 1)

#ezStats(data = prop_correct_subj_replay[sac_suppression_f == "suppressed", ],
      #  wid = .(subj_id.x), dv = .(prop_correct),
       # within = .(stim_dur))

anov_prop_replay
```

Here I start creating the plot for proportion correct and stim_dur [ms]. (N=20)
```{r}
#Moreys Correction for proportion correct
#Removing in-between Variance
prop_correct_subj_replay[, ID_mean := mean(prop_correct), by =.(subj_id.x)]
prop_correct_subj_replay[, overall_mean := mean(prop_correct),]
prop_correct_subj_replay[, p_mean := (prop_correct - ID_mean + overall_mean),]


p_correct_replay <- prop_correct_subj_replay[,
                               .(P_mean = mean(prop_correct), CP_mean = mean(p_mean),  C_SD = sd(p_mean),
                                 C_SE = (sd(p_mean)/sqrt(length(p_mean))), N = length(p_mean)),
                               keyby= .(sac_suppression_f, stim_dur)]



## Standardfehler und Abweichung
prop_correct_subj_replay[, prop_SE := (sd(prop_correct)/sqrt(length(prop_correct))), by =.(subj_id.x, sac_suppression_f)]
prop_correct_subj_replay[, prop_SD := sd(prop_correct), by =.(subj_id.x, sac_suppression_f)]


n_conditions <- length(unique(p_correct_replay$sac_suppression_f))*length(unique(p_correct_replay$stim_dur))
p_correct_replay[, MC_se := C_SE*(n_conditions/(n_conditions-1))]
```



Here I start creating the plot for proportion correct and replay_sac_display_off_lat. (N=20)
```{r}

prop_correct_subj_replay_latency <- ISSPR_data_without_overlap_metrics[ ,
                                                               .(prop_correct = mean(correct),
                                                                 replay_sac_display_off_latency = mean(replay_sac_display_off_latency)),
                                                               by = .(subj_id.x, sac_suppression_f, stim_dur)
                                                              ][order(subj_id.x, sac_suppression_f, stim_dur)]


#Moreys Correction for proportion correct
# Removing in-between Variance
prop_correct_subj_replay_latency[, ID_mean := mean(prop_correct), by =.(subj_id.x)]
prop_correct_subj_replay_latency[, overall_mean := mean(prop_correct),]
prop_correct_subj_replay_latency[, p_mean := (prop_correct - ID_mean + overall_mean),]

p_correct_replay_latency <- prop_correct_subj_replay_latency[,
                               .(P_mean = mean(prop_correct),
                                 CP_mean = mean(p_mean),
                                 C_SD = sd(p_mean),
                                 C_SE = (sd(p_mean)/sqrt(length(p_mean))),
                                 N = length(p_mean),
                                 replay_sac_display_off_latency = mean(replay_sac_display_off_latency)),
                               keyby = .(sac_suppression_f, stim_dur)]


## Standardfehler und Abweichung
prop_correct_subj_replay_latency[, prop_SE := (sd(prop_correct)/sqrt(length(prop_correct))), by =.(subj_id.x, sac_suppression_f)]
prop_correct_subj_replay_latency[, prop_SD := sd(prop_correct), by =.(subj_id.x, sac_suppression_f)]

n_conditions <- length(unique(p_correct_replay_latency$sac_suppression_f))*length(unique(p_correct_replay_latency$stim_dur))
p_correct_replay_latency[, MC_se := C_SE*(n_conditions/(n_conditions-1))]


```

Here is the first plot for proportion correct and replay_display_off_latency
Mara comment: Here i tried to change the color as well (scale_color_manual(values = experiment_colorscale), unluckly the legend changed in a wrong way; How can I solve it?
Should I change here suppressed= filtered; original= unfiltered, so that all plots have the same legend?
Iam afraid that this may be confusing due to the other plots.

Richard: Not sure what you mean by "the legend changed in a wrong way". Is it the order of original/suppressed? If so, then you can use the guide option I used below. 
Generally, indeed, you want to keep the color scale, as well as the associated labels consistent across plots. You can do that easily by updating the levels(mydata$sac_suppression_f), see below. 

```{r}
levels(p_correct_replay_latency$sac_suppression_f) <- c("original", "suppressed") # or something else?

prop_replay_latency_plot <- ggplot(data = p_correct_replay_latency,
                           aes(x = replay_sac_display_off_latency, y = P_mean,
                               color = sac_suppression_f, group = sac_suppression_f)) +
  geom_vline(xintercept = 0, linetype = "dotted", alpha = 0.7) +  # vertikale Linie bei 0
  geom_hline(yintercept = 0.5, linetype = "dotted", alpha = 0.7) +  # horizontale Linie bei 0.5
  geom_errorbar(aes(ymax = P_mean + MC_se, ymin = P_mean - MC_se),
                width = 0, size = 1, alpha = 0.5) +  # Fehlerbalken fr y
  geom_errorbarh(aes(xmax = replay_sac_display_off_latency + MC_se,
                     xmin = replay_sac_display_off_latency - MC_se),
                 height = 0, size = 1, alpha = 0.5) +  # Fehlerbalken fr x
  geom_line(size = 1.5, alpha = 0.8) +  # Linie fr Mittelwerte
  geom_point(size = 2.5) +  # Punkte fr Mittelwerte
  theme_classic(base_size = 12.5) + ocimTheme() +  # klassisches Theme
  coord_cartesian(ylim = c(0.45, 1)) +  # Y-Achsen-Bereich anpassen
  #scale_color_viridis_d(option = "cividis", end = 0.4, direction = -1, guide = guide_legend(reverse = TRUE)) +  # Farbskala
  scale_color_manual(values = experiment_colorscale, guide = guide_legend(reverse = TRUE)) + 
  scale_y_continuous(expand = c(0,0)) +  # Y-Achse ohne zustzliche Abstnde
  scale_x_continuous(breaks = c(-50, -40, -30, -20, -10, 0, 10, 20, 30), limits = c(-50, 30)) +  # X-Achse mit entsprechenden Breaks und Limits
  labs(x = "Display offset re saccade offset [ms]", y = "Proportion scene correctly matched",
       color = "Simulated suppression", fill = "Simulated suppression") +  # Achsenbezeichner
  theme(legend.position = "right")

prop_replay_latency_plot
```

Here I wanna do a ezANOVA for prop_correct_subj_replay_latency
```{r}

prop_correct_subj_replay_latency$stim_dur <- factor(prop_correct_subj_replay_latency$stim_dur)
prop_correct_subj_replay_latency$subj_id.x <- factor(prop_correct_subj_replay_latency$subj_id.x)

anov_prop_replay_latency <- ezANOVA(data = prop_correct_subj_replay_latency, dv = .(prop_correct),
                                    wid = .(subj_id.x), within = .(sac_suppression_f, stim_dur),
                                    detailed = TRUE)
anov_prop_replay_latency
```
Control analyses of saccade metrics (saccade duration, peak velocity, amplitude)
```{r}
ISSP_mean_sac_subj <- issp[experiment_f %in% c(1, 2), .(sac_dur = mean(sac_dur),
                                                         sac_amp = mean(sac_amp),
                                                         sac_vpeak = mean(vpeak),
                                                         sac_display_off_latency = mean(sac_display_off_latency),
                                                         sac_display_latency = mean(sac_display_latency) ),
                            by = .(experiment_f, subj_id, stim_dur_ms_f)]


# correction for between-subject variance
ISSP_mean_sac_subj[ , gm_sac_dur := mean(sac_dur), by = .(experiment_f)]
ISSP_mean_sac_subj[ , gm_sac_amp := mean(sac_amp), by = .(experiment_f)]
ISSP_mean_sac_subj[ , gm_sac_vpeak := mean(sac_vpeak), by = .(experiment_f)]
ISSP_mean_sac_subj[ , sac_dur.w := sac_dur - mean(sac_dur) + gm_sac_dur, by = .(subj_id, experiment_f)]
ISSP_mean_sac_subj[ , sac_amp.w := sac_amp - mean(sac_amp) + gm_sac_amp, by = .(subj_id, experiment_f)]
ISSP_mean_sac_subj[ , sac_vpeak.w := sac_vpeak - mean(sac_vpeak) + gm_sac_vpeak, by = .(subj_id, experiment_f)]


# aggregate to subject level
ISSP_mean_sac <- ISSP_mean_sac_subj[ , .(sac_dur = mean(sac_dur),
                                         sac_dur_sd = sd(sac_dur.w) / sqrt(length(sac_dur)),
                                         sac_amp = mean(sac_amp),
                                         sac_amp_sd = sd(sac_amp.w) / sqrt(length(sac_amp)),
                                         sac_vpeak = mean(sac_vpeak),
                                         sac_vpeak_sd = sd(sac_vpeak.w) / sqrt(length(sac_vpeak)),
                                         sac_display_off_latency = mean(sac_display_off_latency),
                                         sac_display_off_latency_sd = sd(sac_display_off_latency) / sqrt(length(sac_display_off_latency))),
                                       by = .(experiment_f, stim_dur_ms_f)]

```
Here is the Plot for Saccade duration and Exp 1&2
```{r}
dur_xlim_sacmetrics <- c(-60, 30)
p_sac_dur <- ggplot(data = ISSP_mean_sac,
                    aes(x = sac_display_off_latency, y = sac_dur, color = experiment_f)) +
  geom_vline(xintercept = 0, linetype = "dotted", alpha = 0.7) +
  geom_line(data = ISSP_mean_sac_subj,
            aes(x = sac_display_off_latency, y = sac_dur.w, color = experiment_f, group = paste(experiment_f, subj_id)),
            size = 0.5, alpha = 0.2) +
  geom_errorbar(aes(ymax = sac_dur + 2*sac_dur_sd, ymin = sac_dur - 2*sac_dur_sd),
                width = 0, size = 1, alpha = 0.5) +
  geom_errorbarh(aes(xmax = sac_display_off_latency + 2*sac_display_off_latency_sd,
                     xmin = sac_display_off_latency - 2*sac_display_off_latency_sd),
                 height = 0, size = 1, alpha = 0.5) +
  geom_point(size = 1.5) +
  geom_line(size = 1.5) +
  coord_cartesian(expand = FALSE, xlim = dur_xlim_sacmetrics) +
  scale_color_manual(values = experiment_colorscale) +
  scale_fill_manual(values = experiment_colorscale) +
  scale_alpha_manual(values = seq(0.2, 1, length.out = 8)) +
  labs(x = "Display offset re saccade offset [ms]", y = "Saccade\nduration [ms]",
       color = "Experiment", fill = "Experiment") +
  theme_minimal(base_size = 15) + ocimTheme()

p_sac_dur

ezStats(data = ISSP_mean_sac_subj[experiment_f=="1"],
        dv = .(sac_dur), wid = .(subj_id),
        within = .(stim_dur_ms_f) )

ezStats(data = ISSP_mean_sac_subj[experiment_f=="2"],
        dv = .(sac_dur), wid = .(subj_id),
        within = .(stim_dur_ms_f) )
```

Here is the plot for Saccade Velocity and Exp 1&2
```{r}
peak_xlim_sacmetrics <- c(-60, 30)
p_sac_vpeak <- ggplot(data = ISSP_mean_sac,
                    aes(x = sac_display_off_latency, y = sac_vpeak, color = experiment_f)) +
  geom_vline(xintercept = 0, linetype = "dotted", alpha = 0.7) +
  geom_line(data = ISSP_mean_sac_subj,
            aes(x = sac_display_off_latency, y = sac_vpeak.w, color = experiment_f, group = paste(experiment_f, subj_id)),
            size = 0.5, alpha = 0.2) +
  geom_errorbar(aes(ymax = sac_vpeak + 2*sac_vpeak_sd, ymin = sac_vpeak - 2*sac_vpeak_sd),
                width = 0, size = 1, alpha = 0.5) +
  geom_errorbarh(aes(xmax = sac_display_off_latency + 2*sac_display_off_latency_sd,
                     xmin = sac_display_off_latency - 2*sac_display_off_latency_sd),
                 height = 0, size = 1, alpha = 0.5) +
  geom_point(size = 1.5) +
  geom_line(size = 1.5) +
  coord_cartesian(expand = FALSE, xlim = peak_xlim_sacmetrics) +
  scale_color_manual(values = experiment_colorscale) +
  scale_fill_manual(values = experiment_colorscale) +
  scale_alpha_manual(values = seq(0.2, 1, length.out = 8)) +
  labs(x = "Display offset re saccade offset [ms]", y = "Saccade peak\nvelocity [dva/s]",
       color = "Experiment", fill = "Experiment") +
  theme_minimal(base_size = 15) + ocimTheme()
p_sac_vpeak

ezStats(data = ISSP_mean_sac_subj[experiment_f=="1"],
        dv = .(sac_vpeak), wid = .(subj_id),
        within = .(stim_dur_ms_f) )

ezStats(data = ISSP_mean_sac_subj[experiment_f=="2"],
        dv = .(sac_vpeak), wid = .(subj_id),
        within = .(stim_dur_ms_f) )

```

Here is the Plot fr Saccade Amplitude and Exp 1&2
```{r}
amp_xlim_sacmetrics <- c(-60, 30)
p_sac_amp <- ggplot(data = ISSP_mean_sac,
                    aes(x = sac_display_off_latency, y = sac_amp, color = experiment_f)) +
  geom_vline(xintercept = 0, linetype = "dotted", alpha = 0.7) +
  geom_line(data = ISSP_mean_sac_subj,
            aes(x = sac_display_off_latency, y = sac_amp.w, color = experiment_f, group = paste(experiment_f, subj_id)),
            size = 0.5, alpha = 0.2) +
  geom_errorbar(aes(ymax = sac_amp + 2*sac_amp_sd, ymin = sac_amp - 2*sac_amp_sd),
                width = 0, size = 1, alpha = 0.5) +
  geom_errorbarh(aes(xmax = sac_display_off_latency + 2*sac_display_off_latency_sd,
                     xmin = sac_display_off_latency - 2*sac_display_off_latency_sd),
                 height = 0, size = 1, alpha = 0.5) +
  geom_point(size = 1.5) +
  geom_line(size = 1.5) +
  coord_cartesian(expand = FALSE, xlim = amp_xlim_sacmetrics) +
  scale_color_manual(values = experiment_colorscale) +
  scale_fill_manual(values = experiment_colorscale) +
  scale_alpha_manual(values = seq(0.2, 1, length.out = 8)) +
  labs(x = "Display offset re saccade offset [ms]", y = "Saccade\namplitude [dva]",
       color = "Experiment", fill = "Experiment") +
  theme_minimal(base_size = 15) + ocimTheme()
p_sac_amp

ezStats(data = ISSP_mean_sac_subj[experiment_f=="1"],
        dv = .(sac_amp), wid = .(subj_id),
        within = .(stim_dur_ms_f) )

ezStats(data = ISSP_mean_sac_subj[experiment_f=="2"],
        dv = .(sac_amp), wid = .(subj_id),
        within = .(stim_dur_ms_f) )


```

Here I wanna do the histogramm for number of trials and display duration for Exp. 1&2
```{r}
histo_xlim_pres <- c(-70, 60)

# first, present the metric display offset re saccade offset
p_histo12 <- ggplot(data = issp %>% filter(experiment %in% c(1, 2)), aes(x = sac_display_off_latency,
                                               color = experiment_f, group = paste(stim_dur_ms_f, experiment_f),
                                               alpha = stim_dur_ms_f)) +
  geom_hline(aes(color = experiment_f, yintercept = 0), size = 2) +
  geom_vline(xintercept = 0, linetype = "dotted", alpha = 0.7) +
  geom_freqpoly(binwidth = 4, size = 1.5) +
  #geom_density(size = 1.5) +
  coord_cartesian(expand = FALSE, xlim = histo_xlim_pres ) +
  scale_color_manual(values = experiment_colorscale) +
  scale_fill_manual(values = experiment_colorscale) +
  scale_alpha_manual(values = seq(0.2, 1, length.out = 8)) +
  labs(x = "Display offset re saccade offset [ms]", y = "Number of trials",
       color = "Experiment", fill = "Experiment", alpha = "Display\nduration [ms]") +
  theme_minimal(base_size = 15) + ocimTheme() +
  facet_wrap(~experiment_f, nrow = 3, scales = "free_y", strip.position = "right") + guides(color = "none")
p_histo12
```

Here I wanna do the frequency plot for the mean distribution of all samples and observers for replay
no vari. times for all observers, no individual saccade statistics
Mara Comment: False color scale and false plot (did I use the false data)?

Richard: Well, yes, you use the wrong data, that is, the aggregated data (one point per condition). To compute proper histograms, you'd need the trial-resolved data. I'm not sure what you ultimately what to plot but I guess you want to replicate the plot above? I have only changed the basic, this plot still needs work (color scale, labels, theme etc).

Again: the color scale in the plot above is the same you use to compare original vs suppressed. Make sure this can be visually disentangled. Also, the plot is basically the one from the manuscript and I'm not sure whether that's a good idea with Martin and Sven as your referees. 

```{r}
plot_freq <- ggplot(data = ISSPR_data_without_overlap_metrics %>%
                      filter(experiment == 4),  # Zeige nur das Replay-Experiment
                    aes(x = replay_sac_display_off_latency,
                        color = factor(stim_dur_ms_f),  # Farbe fr Display-Dauer
                        group = stim_dur_ms_f)) +
  geom_hline(yintercept = 0, size = 2, color = "gray60") +
  geom_vline(xintercept = 0, linetype = "dotted", alpha = 0.7) +
  geom_freqpoly(binwidth = 4, size = 1.5) +
  coord_cartesian(expand = FALSE, xlim = c(-70, 60)) +
  scale_color_viridis_d(name = "Display\nduration [ms]") +  # Farbskala
  labs(x = "Display offset re saccade offset [ms]",
       y = "Number of trials") +
  theme_minimal(base_size = 15) +
  ocimTheme() +
  theme(plot.margin = margin(t = 10, r = 10, b = 10, l = 10),
        legend.box.margin = margin(5, 5, 5, 5))

plot_freq
```

Here I wanna make predictions of saccade data related to replay (within-subject); how strong are the datapoints related to each other?

Mara Comment: Need help here pls

Richard: Sorry, not sure I understand. You want to correlate proportion correct in the saccade exp and proportion correct in the replay exp, matched by condition? I guess I could write this code for you (which is not the goal), but as this is exploratory and you still have other stuff to do, I'd suggest we postpone this and work on this together if you still have time. 

```{r}

# 
# lmer(replay_sac_display_off_latency ~ sac_display_off_latency + (1 | common_subj_id), data = subset_ISSPexperiments)
# 
# #other option Pearson correlation
# pearson_ISSPR <- cor.test(subset_ISSPexperiments$sac_display_off_latency,
#                              subset_ISSPexperiments$replay_sac_display_off_latency,
#                              method = "pearson")
# pearson_ISSPR
# 
# #repeated measures Korrelation
# #library(rmcorr)
# #rmcorr_ISSPR <- rmcorr(participant = common_subj_id,
#                        # measure1 = sac_display_off_latency,
#                        # measure2 = replay_sac_display_off_latency,
#                        # data = subset_ISSPexperiments)
# 
# rmcorr_ISSPR
```


Here this is not needed for the master thesis
Here we will create BINS for the latency
```{r}
ISSPR_data_without_overlap_metrics[, sac_display_off_latency_bins := cut_number(replay_sac_display_off_latency, n=4)]


prop_correct_subj_bins_replay <- ISSPR_data_without_overlap_metrics[ , .(prop_correct = mean(correct)),
                                by = .(subj_id.x, sac_suppression_f, sac_display_off_latency_bins)][order(subj_id.x, sac_suppression_f, sac_display_off_latency_bins)]


prop_correct_subj_bins_replay$sac_suppression_f <- ordered(prop_correct_subj_bins_replay$sac_suppression_f)
```
Here we will create the Plot for BINS
```{r}
p_prop_correct_subj_bins_replay <- ggplot(data = prop_correct_subj_bins_replay,
                                   aes(x = sac_display_off_latency_bins, y = prop_correct,
                                       color = sac_suppression_f, group = sac_suppression_f)) +
  geom_point() + geom_line() +
  theme_classic() +
  labs(x = "Display offset re simulated saccade offset", y = "Proportion correct",
       color = "Simulated suppression") +
  facet_wrap(~subj_id.x)

p_prop_correct_subj_bins_replay

```
Here we will have the ezANOVA 2 for the BINS
```{r}
prop_correct_subj_bins_replay$subj_id.x <- factor(prop_correct_subj_bins_replay$subj_id.x)
anov_prop_bins_replay <- ezANOVA(data = prop_correct_subj_bins_replay, dv =prop_correct, wid = subj_id.x,
                          within=.(sac_suppression_f,sac_display_off_latency_bins),
                          detailed = TRUE)

anov_prop_bins_replay
```

Morey Korrektur incl Cousineau for BINS
```{r}
prop_correct_subj_bins_replay[, ID_mean := mean(prop_correct), by =.(subj_id.x)]
prop_correct_subj_bins_replay[, overall_mean := mean(prop_correct),]
prop_correct_subj_bins_replay[, p_mean := (prop_correct - ID_mean + overall_mean),]

p_correct_bins_replay <- prop_correct_subj_bins_replay[,
                                         .(P_mean = mean(prop_correct), CP_mean = mean(p_mean),  C_SD = sd(p_mean),
                                           C_SE = (sd(p_mean)/sqrt(length(p_mean))), N = length(p_mean)),
                                         keyby= .(sac_suppression_f, sac_display_off_latency_bins)]



# SD und Abweichung
prop_correct_subj_bins_replay[, prop_SE := (sd(prop_correct)/sqrt(length(prop_correct))), by =.(subj_id.x, sac_suppression_f)]
prop_correct_subj_bins_replay[, prop_SD := sd(prop_correct), by =.(subj_id.x, sac_suppression_f)]


n_conditions_bins <- length(unique(p_correct_bins_replay$sac_suppression_f))*length(unique(p_correct_bins_replay$sac_display_off_latency_bins))
p_correct_bins_replay[, MC_se := C_SE*(n_conditions_bins/(n_conditions_bins-1))]

```
Second Plot for BINS
```{r,warning=FALSE}
prop_bins_replay <- ggplot(data = p_correct_bins_replay,
                 aes(x = sac_display_off_latency_bins,
                     y = P_mean,
                     color = sac_suppression_f, fill = sac_suppression_f, group = sac_suppression_f)) +

  geom_hline(yintercept = 0.5,linetype='dashed')+
  geom_line(size = 1.5, alpha = 0.8) +
  geom_point(alpha = 0.8, size = 3) +
  geom_ribbon(aes(ymin = P_mean - MC_se,
                  ymax = P_mean + MC_se), color = NA, alpha = 0.3) +
  scale_y_continuous(expand=c(0,0),limits=c(0.45,1))+
  scale_fill_viridis_d(option = "cividis", end = 0.4, direction = -1, guide = guide_legend(reverse = TRUE)) +
  scale_color_viridis_d(option = "cividis", end = 0.4, direction = -1, guide = guide_legend(reverse = TRUE)) +
  theme_classic(base_size = 15) + ocimTheme() +
  labs(x = "Display offset re simulated saccade offset",y = "Proportion correct",
       fill = "Image type", color = "Image type") +
  theme(legend.position = "right")

prop_bins_replay


```
Here we will run some other des. statistics
```{r}
ezStats(data = ISSPR_data_without_overlap_metrics[experiment=="4"],
        dv = .(replay_sac_display_latency), wid = .(subj_id.x),
        within = .(stim_dur) )


ezStats(data = ISSPR_data_without_overlap_metrics[experiment=="4"],
        dv = .(replay_sac_dur), wid = .(subj_id.x),
        within = .(stim_dur) )

anov_replay_sac_dur <- ezANOVA(data = ISSPR_data_without_overlap_metrics[experiment=="4"],
        dv = .(replay_sac_dur), wid = .(subj_id.x),
        within = .(stim_dur), detailed = TRUE)

```
Here we will figure out the effect of suppression and the task
```{r}
ISSPR_suppression_correct <- ISSPR_data_without_overlap_metrics[ , .(prop_correct = mean(correct),
                                               replay_sac_display_off_latency = mean(replay_sac_display_off_latency)),
                            by = .(subj_id.x, sac_suppression_f, stim_dur)]


ISSPR_suppression_correct [ , stim_dur := ordered(stim_dur)]

#Morey Korrektur incl Cousineau fr suppression and task
ISSPR_suppression_correct[, ID_mean := mean(prop_correct), by =.(subj_id.x)]
ISSPR_suppression_correct[, overall_mean := mean(prop_correct),]
ISSPR_suppression_correct[, p_mean := (prop_correct - ID_mean + overall_mean),]

p_correct_suppression <- ISSPR_suppression_correct[,
                                                       .(P_mean = mean(prop_correct), CP_mean = mean(p_mean),  C_SD = sd(p_mean),
                                                         C_SE = (sd(p_mean)/sqrt(length(p_mean))), N = length(p_mean)),
                                                       keyby= .(sac_suppression_f, replay_sac_display_off_latency)]



# SD und Abweichung
ISSPR_suppression_correct[, prop_SE := (sd(prop_correct)/sqrt(length(prop_correct))), by =.(subj_id.x, sac_suppression_f)]
ISSPR_suppression_correct[, prop_SD := sd(prop_correct), by =.(subj_id.x, sac_suppression_f)]


n_conditions_supp <- length(unique(p_correct_suppression$sac_suppression_f))*length(unique(p_correct_suppression$replay_sac_display_off_latency))
p_correct_suppression[, MC_se := C_SE*(n_conditions_supp/(n_conditions_supp-1))]
```


Here we will have two dimensions (saccade duration and saccade amplitude) for each subject
by mean
```{r}
ISSPR_data_without_overlap_metrics[, sac_amp_n := cut_number(sac_amp, n=10)]
ISSPR_data_without_overlap_metrics[, sac_dur_bins := cut_number(sac_dur, n=2)]
table(ISSPR_data_without_overlap_metrics$subj_id.x,
      ISSPR_data_without_overlap_metrics$sac_dur_bins)

metrics_subj_bins_replay_dur <- ISSPR_data_without_overlap_metrics[ , .(sac_dur_f = mean(sac_dur),
                                                                        disp_off_re_sac_off = mean(replay_sac_display_off_latency),
                                                                        correct = mean(correct)),
                                                                by = .(subj_id.x, sac_dur_bins, stim_dur)]
metrics_subj_bins_replay_dur[ , sac_dur_f2 := mean(sac_dur_f), by = .(subj_id.x, sac_dur_bins)]
```
Here is the plot of sac_dur and sac_amp
```{r}
ggplot(data = metrics_subj_bins_replay_dur,
       aes(x = disp_off_re_sac_off,
           #x = as.numeric(stim_dur),
           y = correct,
           color = sac_dur_f, group = sac_dur_f2 )) +
  geom_hline(yintercept = 0.5, linetype = "dotted") +
  geom_vline(xintercept = 0, linetype = "dotted") +
  geom_point() + geom_line() +
  theme_classic() +
  labs(x = "Display offset re saccade offset", y = "Proportion correct",
       color = "Sacc. duration") +
  facet_wrap(~subj_id.x)

```
